---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# saperlipopette

<!-- badges: start -->
[![R-CMD-check](https://github.com/maelle/saperlipopette/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/maelle/saperlipopette/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

The goal of saperlipopette is to hold functions creating Git messes, that users 
would then solve, to follow https://ohshitgit.com/.

## Installation

You can install the development version of saperlipopette like so:

``` r
pak::pak("maelle/saperlipopette")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library("saperlipopette")
parent_path <- withr::local_tempdir()
path <- one_small_change(parent_path) # to be solved with ?one_small_change
# what's in path
fs::dir_tree(path)
gert::git_log(repo = path)
```

At this stage, the user would read the example in `?one_small_change`, 
to know what to do, 
and would follow the URL in that same manual page, to find the corresponding ohshitgit entry.
In practice here the user would change a file, then Git add it, then run `git commit --amend --no-edit`.
The user would examine the Git history before and after this.
We might want to refine that interface somehow, maybe with cli messages instead of relying on the manual page.

We've set the Git author and commiter so that the automatic commits get the same 
hashes, which can be useful when teaching a group: everyone should be looking at the same hashes on their machine.

```{r example2}
parent_path <- withr::local_tempdir()
path <- one_small_change(parent_path)
gert::git_log(repo = path)
parent_path2 <- withr::local_tempdir()
path2 <- one_small_change(parent_path2)
gert::git_log(repo = path2)
```
