---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# saperlipopette

<!-- badges: start -->
[![R-CMD-check](https://github.com/maelle/saperlipopette/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/maelle/saperlipopette/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

The goal of saperlipopette is to hold functions creating Git messes, that users 
would then solve, to follow https://ohshitgit.com/.

## Installation

You can install the development version of saperlipopette like so:

``` r
pak::pak("maelle/saperlipopette")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library("saperlipopette")
parent_path <- withr::local_tempdir()
path <- exo_one_small_change(parent_path)
# what's in path
fs::dir_tree(path)
gert::git_log(repo = path)
```

At this stage, the user would open the newly created R project,
where messages would indicate them what to do, 
an which URL to follow, to find the corresponding ohshitgit entry.
In practice here the user would change a file, then Git add it, then run `git commit --amend --no-edit`.
The user would examine the Git history before and after this.

```{r, echo=FALSE}
source(system.file("exo_one_small-change-Rprofile.R", package = "saperlipopette"))
```

That interface relies on adding an `.Rprofile` to the newly created project,
with instructions formatted with the cli package.

We've set the Git author, committer and date so that the automatic commits get the same 
hashes, which can be useful when teaching a group: everyone should be looking at the same hashes on their machine, except for those commits they create themselves.

```{r example2}
parent_path <- withr::local_tempdir()
path <- exo_one_small_change(parent_path)
gert::git_log(repo = path)
parent_path2 <- withr::local_tempdir()
path2 <- exo_one_small_change(parent_path2)
gert::git_log(repo = path2)
```
